Cooperation Is Provably Required in a Version of the Noisy Iterated Prisoner's Dilemma

### 2020-05-20 paper/paper.tex
some more changes

      We construct $C_2$ as follows. First, it finds out in finite time what action $A$ that $s_1$ will take at some large finite future time $T$ (with probability $1 - O(p)$). 
      After that, it responds with the opposite action (which we will denote by $\bar{A}$) right after time $T$. 
      If $s_2$ subsequently perceives that its opponent takes action $A$, it will transition into a copy of $C_1$, the absorbing strongly connected component that $C_2$ replaces. On the other hand, if $s_2$ perceives its opponent taking action $\bar{A}$, then it will transition into an absorbing strongly connected component that always cooperates. A schematic view of $C_2$ is presented in figure ????. This concludes the construction of $s_2$.

>>>>

      We construct $C_2$ as follows. First, it finds out in finite time what action $A$ that $s_1$ will take at some large finite future time $T$ (with probability $1 - O(p)$). 
      \todo{THIS DOESN'T WORK. The problem is the circulation states: if $s_2$ goes into an absorbing SCC before $s_1$ does, our modified $C_2$ might affect the probabilities of $s_1$ going into certain absorbing SCCs. I think a way to fix that is as follows: You take $C_1$, and replace each of its individual states by an SCC, targeting a particular non-absorbing SCC of $s_1$. Make sure that they circulate in sync with each other. That means that we will be able to delay getting into the identification stage of $C_2$ which is exactly what we want.}
      After that, it responds with the opposite action (which we will denote by $\bar{A}$) right after time $T$. 
      If $s_2$ subsequently perceives that its opponent takes action $A$, it will transition into a copy of $C_1$, the absorbing strongly connected component that $C_2$ replaces. On the other hand, if $s_2$ perceives its opponent taking action $\bar{A}$, then it will transition into an absorbing strongly connected component that always cooperates. A schematic view of $C_2$ is presented in figure ????. This concludes the construction of $s_2$.
